How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-11 manuscript/draft_manuscript.Rmd
Update draft_manuscript.Rmd

There were 28,008 downloaded studies, and 9,632 (34%) had a statistical methods section. 
The numbers of excluded studies are shown in Figure~X. 
Of the 12,700 eligible applications, 9523 (75%) had a statistic section.

The odds ratios and 95% credible intervals are shown in Table~X.

@@

Some of the sections were only one word, including "ANOVA", "t-test", "SPSS" and even "SSPS". The median length of the section was 129 words with an inter-quartile range of 71 to 219 words.

>>>>

There were 28,008 downloaded studies. The numbers of excluded studies are shown in Figure~X. 
Of the 12,700 eligible applications, 9523 (75%) had a statistic section.

We examined if four study characteristics predicted a missing statistics section. The odds ratios and 95% credible intervals are in Table~X. Observational studies were less likely to have a missing methods section compared with interventional studies. Missing sections become less likely over time. Studies with more funders and a larger target sample size were less likely to have a missing methods section.

@@

Some of the statistics sections were only one word, including "ANOVA", "t-test", "SPSS" and even "SSPS". The median length of the section was 129 words with an inter-quartile range of 71 to 219 words.
